---
title: "README"
author: "Kenneth Rose"
date: "Friday, August 08, 2014"
output: 
  md_document:
    variant: markdown_github
---

## Intro

This package is an R wrapper for the Syspower SKM API.

## Install and load

Install the package from github.

```
if(!require("devtools")) install.packages("devtools")
library("devtools")
install_github("krose/skm")
```

Load the package. I'll also load the ggplot2 package, to make fancier plots.

```{r}
library("skm")
```

## Web Query data


### ENOQ4-14

Let's load the daily closing prices for the contract ENOQ4-14 in 2014.

```{r, echo=TRUE}
q414 <- skm_webquery(user_id = user_id, user_password = user_password, series_name = "NPENOQ414", interval = "day", start_time = "01-01-2014", end_time = "0")
str(q414)
```


### SPOT SYS and DK1 daily

Let's take a look at the SPOT for the system and DK1. Notice i query more than one series.

```{r}
spot <- skm_webquery(user_id = user_id, user_password = user_password, series_name = c("SPOT", "SPOTDK1"), interval = "day", start_time = "01-01-2014", end_time = "0")
str(spot)

```

### SPOT SYS and DK1 hourly

And then there is hourly SPOT. Notice the start time.

```{r}
spot <- skm_webquery(user_id = user_id, user_password = user_password, series_name = c("SPOT", "SPOTDK1"), interval = "Hour", start_time = "w-2", end_time = "0")
str(spot)

```



## UMM Query data

Here are just a few examples:


```{r}
## transmission

str(skm_ummquery(user_id = user_id, user_password = user_password, interval = "week", start_time = "2014-08-01", end_time = "2014-08-31", accrow = "no", type = "transmission", areas = c("Sweden", "Denmark"), internalorfuels = "no"))


## production
str(skm_ummquery(user_id = user_id, user_password = user_password, interval = "hour", start_time = "2014-08-01", end_time = "2014-08-31", accrow = "no", type = "production", areas = "Nordpool", internalorfuels = "Nuclear"))


## station
str(skm_ummquery(user_id = user_id, user_password = user_password, interval = "day", start_time = "2014-08-01", end_time = "2014-08-31", accrow = "no", type = "station", areas = NULL, internalorfuels = 3))
```

